---
title: "p8105_hw2_bg2715"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Problem 1

Loading data.
```{r}
data("instacart")
instacart %>%
  head(3)
```
Short description:
This dataset has 1384617 rows and 15 columns. Each row represent a single item ordered and each column represent a feature/information of that order. Key variables are "aisle", "product_name", "order_dow", "order_hour_of_day" and so on. For example, the first line means user 112108 ordered bulgarian yogurt from aisle yogurt in department dairy eggs at ten o'clock on Thursday.
```{r}
ai_df = instacart %>%
  count(aisle) %>%
  arrange(-n)
  knitr::kable(head(ai_df[1:4, ]))
```

There are 134 aisles and the most items ordered from "fresh vegetables" and "fresh fruits" aisles.

```{r}
ai_plot = instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  arrange(n) 

ggplot(ai_plot, aes(x = aisle, y = n)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0.5))
  
```

Most of them are less than 40000.

```{r}
bdp_df = instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%  
  group_by(aisle, product_name) %>%
  summarise(n_times = n()) %>%
  top_n(n = 3)
  knitr::kable(bdp_df)
```

The most popular item in “baking ingredients”, “dog food care”, and “packaged vegetables fruits” is "Light Brown Sugar" (499), "Snack Sticks Chicken & Rice Recipe Dog Treats" (30) and "Organic Baby Spinach" (9784) respectively.

```{r}
pc_df = instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarise(mean_hour = mean(order_hour_of_day)) %>%
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) 

colnames(pc_df) = c('product_name', 'Sun', 'Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat')
knitr::kable(pc_df)
```
The mean hour of ordering of coffee ice cream is greater than that of pink lady apples except for Friday.

